% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{setspace}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zhenlin Huang}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{zhlinhng@gmail.com}{(+1) 650-667-5006}{http://www.zhenlin.me}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}
 
\section{\faGraduationCap\ EDUCATION}
\datedsubsection{\textbf{Xidian University}, Xi'an, China}{2014 -- Present}
\textit{Master student} Communication Engineering, expected June 2017
\datedsubsection{\textbf{Xidian University}, Xi'an, China}{2010 -- 2014}
\textit{B.S.} Communication Engineering

\section{\faTrophy\ HONORS \& AWARDS}
\begin{onehalfspacing}
\datedline{\textit{School \nth{1} Prize}, Academic Scholarship }{Nov. 2013}
\datedline{National Computer Rank Examination Certificate}{Dec. 2012}
\datedline{\textit{School \nth{1} Prize}, Model Contest for College Students}{Dec. 2012}
\end{onehalfspacing}


\section{\faCogs\ SKILLS}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages:}\ \textbf{Java, Android,} (HTML, CSS, JavaScript, MySQL, Python) 
  \item \textbf{Platform:}\ Linux, OpenWrt Embedded Systems, Windows
  \item \textbf{Development Tools:}\ Vim, AndroidStudio
  \item \textbf{English Level:}\ CET-6 (449)
\end{itemize}

\section{\faUsers\ EXPERIENCE}
\datedsubsection{\textbf{PTP-1588 Virtual Machine Synchronization System}}{Sep. 2015 -- Present}
\role{Team leader}{China state shipbuilding corporation 709th institute project}
\setlength{\parindent}{2em}Improve the time synchronization precision of virtual machine
\begin{onehalfspacing}
\begin{itemize}[leftmargin=5em]
  \item Based on IEEE 1588 protocol, and demand for the characteristics of virtual clusters, propose appropriate time synchronization programs, and that the program meets the synchronization accuracy.
  \item Propose and implement synchronous measurement scheme based on and PTP server and client card.
  \item Optimize synchronization effect of virtual machine on the basis of the of PTPd software.
  \item Implementation hardware-based synchronization scheme supports a single physical machine running multiple virtual machines simultaneously.
\end{itemize}
\end{onehalfspacing}

\datedsubsection{\textbf{A Peer-to-Peer Instant Messaging and Positioning System}}{Apr. 2015 -- Nov. 2015}
\role{Team member}{Individual Project}
\setlength{\parindent}{2em}Implement instant communication positioning system for mobile terminal
\begin{onehalfspacing}
\begin{itemize}[leftmargin=5em]
  \item Design a P2P instant messaging system on the Android platform with the integration of indoor positioning module.
  \item Use two positioning methods, including coarse-grained anchor-based positioning and fine-grained RSSI-based positioning.
  \item Achieve the P2P instant messaging capabilities on the Android platform, to provide users with three basic forms(text, voice and image) of communication. 
\end{itemize}
\end{onehalfspacing}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faEnvelopeO\ MISCELLANEOUS}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item \textbf{LinkedIn:}\ https://www.linkedin.com/in/zhlinh
  \item \textbf{GitHub:}\ https://github.com/zhlinh
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
